### 2012-04-29 trunk/GUIErrorDetector/paper/abstract.tex
many tweaks
make some format adjustment

This paper presents a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph reachability problem with
thread spawning as the sources and GUI object accessing as the sinks. 
Standard call graph construction algorithms fail to build a good
call graph for some modern GUI applications, because of heavy use of reflection.
Thus, we present a method to build reflection-aware call graphs.

We implemented our technique and instantiated it for four popular Java GUI
platforms: SWT, the Eclipse plugin development framework, Swing, and
Android. In an evaluation on \subnum programs comprising \totaloc LOC, our technique
found both previously-known and unknown errors.

@@

>>>>

This paper presents a general technique to find such \textit{invalid thread access}
errors in multithreaded GUI applications. We formulate finding invalid
thread access errors as a call graph reachability problem with
thread spawning as the sources and GUI object accessing as the sinks. 
Standard call graph construction algorithms fail to build a good
call graph for some modern GUI applications, because of heavy use of reflection.
Thus, our technique builds reflection-aware call graphs.

We implemented our technique and instantiated it for four popular Java GUI
frameworks: SWT, the Eclipse plugin framework, Swing, and
Android. In an evaluation on \subnum programs comprising \totaloc LOC, our technique
found 5 previously-known errors and 7 new ones.

@@

\smallskip
\noindent
\textbf{Categories and Subject Descriptors}:  
D.2.5 [Software Engineering]: Testing and Debugging.
\\
\textbf{General Terms: }
Reliability, Experimentation.
\\
\textbf{Keywords: }
Static analysis, invalid thread access error.

### 2012-04-29 trunk/GUIErrorDetector/paper/introduction.tex
make some format adjustment

%\subsection{The Single-thread Rule for GUI Object Access}
%ugly hack
\subsection{\hspace{-1.1ex}\mbox{The}~\mbox{Single-thread}~\mbox{Rule}~\mbox{for}~\mbox{GUI}~\mbox{Object}~\mbox{Access}}

Many popular GUI frameworks such as Swing~\cite{swing}, SWT~\cite{swt}, Eclipse plugin~\cite{eclipse},
Android~\cite{android}, Qt~\cite{qt}, and MacOS Cocoa~\cite{macos}
adopt the \textit{single-GUI-thread rule}:

>>>>

%\subsection{The Single-thread Rule for GUI Object Access}
%ugly hack
%\subsection{\hspace{-1.1ex}\mbox{The}~\mbox{Single-thread}~\mbox{Rule}~\mbox{for}~\mbox{GUI}~\mbox{Object}~\mbox{Access}}

\subsection{The Single-thread Rule}

Many popular GUI frameworks such as Swing~\cite{swing}, SWT~\cite{swt}, Eclipse plugin~\cite{eclipse},
Android~\cite{android}, Qt~\cite{qt}, and MacOS Cocoa~\cite{macos}
adopt the \textit{single-GUI-thread rule} for GUI object access:
